miniKanren with fair search strategies

### 2019-04-08 Paper/paper.tex
adding reasoned 2th bib

When every sub-goal of a disjunction produces infinite states, the existing 
disjunctive operator allocates half computational effort to its first goal, 
quater to the second, eighth to the third, and so on. The unfairness provides 
both opportunity and burden: miniKanren users can place more frequently used 
goal at the beginning to optimize their programs; however, it might be a 
catastrophe if a goal that generate many useless states is placed before more 
important goals. Seasoned miniKanreners usually know how to utilize 
the unfairness to optimize their programs. However, we believe search strategies 
that is less sensitive to goal order can also be useful to little miniKanreners 
as well as seansoned ones. We propose two such search strategies, balanced 
interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
affect the efficiency and the answer order of known miniKanren programs. The 
experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
2nd Edition}.

>>>>

Interleaving DFS, the search strategy of \texttt{cond$^e$} in
miniKanren~\citep{friedman_reasoned_2018}, allocates computational resource
by the order in which the claueses are written. Each clause of a
\texttt{cond$^e$} takes a half of the current resource and passes the other half
to its following clauses, except for the last clause that takes all of current
resource. 
both opportunity and burden: miniKanren users can place more frequently used 
goal at the beginning to optimize their programs; however, it might be a 
catastrophe if a goal that generate many useless states is placed before more 
important goals. Seasoned miniKanreners usually know how to utilize 
the unfairness to optimize their programs. However, we believe search strategies 
that is less sensitive to goal order can also be useful to little miniKanreners 
as well as seansoned ones. We propose two such search strategies, balanced 
interleaving DFS (biDFS) and breadth-first search (BFS), and observe how they 
affect the efficiency and the answer order of known miniKanren programs. The 
experiment is conducted with the miniKanren from \textit{The Reasoned Schemer, 
2nd Edition}.
